Figures

### 2025-02-19 Figures/PaperFiguresextended.Rmd
Added code for S6

##################################################################################################################
Scailyte part
#Supplementary Data Figure 6a, b
```{r barplot distribution of cv splits, all cells, prolif}
meta <- read.csv("/home/common/data/output/projects/ENDO/E042/A001/summary_plots_cv_splits/metadata_prolif_eval_fold_all.csv")

@@

Supplementary Data Figure 6c
```{r}

>>>>

#Supplementary Data Figure 6a, b
#Need to change path
```{r barplot distribution of cv splits, all cells, prolif}
meta <- read.csv("/home/common/data/output/projects/ENDO/E042/A001/summary_plots_cv_splits/metadata_prolif_eval_fold_all.csv")

#Supplementary Data Figure 6a
# reshape df
melted_meta <- melt(meta, id.vars = c("lane", "endo_grade"), measure.vars = c("fold1", "fold2", "fold3", "fold4", "fold5"))
## create the bar plot for endo_EndometriosisGrade
SFig6a <- ggplot(melted_meta, aes(x = variable, fill = endo_grade)) +
  geom_bar(position = "stack", width = 0.7) +
  facet_wrap(~ fct_rev(value), ncol = 2) +
  labs(title = "Bar Plot of Samples by Endo EndometriosisGrade",
       x = "Fold",
       y = "Number of Samples") +
  scale_fill_manual(values = c("severe" = "red", "mild" = "orange", "CTL" = "blue")) +
  theme_minimal() +
  coord_flip()
SFig6a
ggsave(paste0(dir_out,"SFig6a_barplot.pdf"), plot = SFig6a, height = 6.3, width = 7.2)

#Supplementary Data Figure 6b
SFig6b <- ggplot(melted_meta, aes(x = variable, fill = lane)) +
  geom_bar(position = "stack", width = 0.7) +
  facet_wrap(~ fct_rev(value), ncol = 2) +
  labs(title = "Bar Plot of Samples by lane",
       x = "Fold",
       y = "Number of Samples") +
  #scale_fill_manual(values = c("severe" = "red", "mild" = "orange", "CTL" = "blue")) +
  theme_minimal() +
  coord_flip()
SFig6b
ggsave(paste0(dir_out,"SFig6b_barplot.pdf"), plot = SFig6b, height = 6.3, width = 7.2)

Supplementary Data Figure 6c
#Need to change path
```{r}

##################################################################################################################
Scailyte part, extra code to delete

#Supplementary Data Figure 6a, b
```{r barplot distribution of cv splits, all cells, prolif}
meta <- read.csv("/home/common/data/output/projects/ENDO/E042/A001/summary_plots_cv_splits/metadata_prolif_eval_fold_all.csv")

@@
